%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% UMB-CS110-2015S: Introduction to Computing
% Copyright 2015 Pejman Ghorbanzade <pejman@ghorbanzade.com>
% Creative Commons Attribution-ShareAlike 4.0 International License
% More info: https://github.com/ghorbanzade/UMB-CS110-2015S
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def \topDirectory {.}
\def \texDirectory {\topDirectory/src/main/tex}

\documentclass[12pt,letterpaper,twoside]{article}
\usepackage{\texDirectory/template/style/directives}
\usepackage{\texDirectory/template/style/assignment}
\input{\texDirectory/template/config}

\begin{document}

\doc{title}{Lab Session Problems}
\doc{points}{0}

\prepare{header}

\subsection*{Week 5}
\hfill \textbf{March 5, 2015}

Consider a two-dimensional array matrix with $11$ rows and $11$ columns, corresponding to a Cartesian plot with x axis $[-10, 10]$ and y-axis $[-10, 10]$. Initialize this matrix such that each element in matrix is zero. Imagine that the matrix corresponds to a $11$ meters in $11$ meters map that represents footsteps of a subject in real-world. It means all elements of the matrix in which the subject is or has been is shown with one and all square-meters that the person has not visited yet is shown with zero. Imagine that someone is initially at position \texttt{matrix[6][6]}.
\begin{enumerate}[itemsep=0pt]
\item At every instance of time, a random number between $1$ and $4$ is generated and based on generated number the person decides to go up, right, bottom or left. Generate such number and imagine the subject has moved in corresponding direction. Show current footsteps of the person in a program \texttt{MagicWorld1.java}.
\item Write a program \texttt{MagicWorld2.java} that computes how many moves it would take until the person reaches an element on the edge of the world.
\item Modify the previous program to \texttt{MagicWorld3.java} such that when the person moves in one direction, doesn't go back in that direction in his next step. How many moves would it take in this scenario that the person reaches the edge of the world.
\item Try to modify your program to \texttt{MagicWorld4.java} that presents an algorithm that can maximize the number of movements it takes that the person reaches the edge of the world.
\end{enumerate}

\end{document}
