% -----------------------------------------------------------------------------
% The MIT License (MIT)
%
% Copyright (c) 2015 Pejman Ghorbanzade
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
% THE SOFTWARE.
% -----------------------------------------------------------------------------

\def \topDirectory {../..}

\documentclass[12pt,letterpaper,twoside]{article}
\usepackage{\topDirectory/template/style/assignment}

\begin{document}

\input{\topDirectory/template/config}

\doc{title}{Lab Session Problems}
\doc{points}{0}

\prepare{header}

\subsection*{Week 5}
\hfill \textbf{March 5, 2015}

Consider a two-dimensional array matrix with $11$ rows and $11$ columns, corresponding to a Cartesian plot with x axis $[-10, 10]$ and y-axis $[-10, 10]$. Initialize this matrix such that each element in matrix is zero. Imagine that the matrix corresponds to a $11$ meters in $11$ meters map that represents footsteps of a subject in real-world. It means all elements of the matrix in which the subject is or has been is shown with one and all square-meters that the person has not visited yet is shown with zero. Imagine that someone is initially at position \texttt{matrix[6][6]}.
\begin{enumerate}[itemsep=0pt]
\item At every instance of time, a random number between $1$ and $4$ is generated and based on generated number the person decides to go up, right, bottom or left. Generate such number and imagine the subject has moved in corresponding direction. Show current footsteps of the person in a program \texttt{MagicWorld1.java}.
\item Write a program \texttt{MagicWorld2.java} that computes how many moves it would take until the person reaches an element on the edge of the world.
\item Modify the previous program to \texttt{MagicWorld3.java} such that when the person moves in one direction, doesn't go back in that direction in his next step. How many moves would it take in this scenario that the person reaches the edge of the world.
\item Try to modify your program to \texttt{MagicWorld4.java} that presents an algorithm that can maximize the number of movements it takes that the person reaches the edge of the world.
\end{enumerate}

\end{document}
